---
title: "Where are Torontonians likely to get married?"
subtitle: "Analysing the different marriage offices around GTA"
author: 
  - Aamishi Avarsekar
thanks: "Code and data are available at: https://github.com/aamishi/marriages_weekly_reflection/tree/master"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
```


# Introduction

In this week's reflection exercise, I will take a look at where people from GTA are most likely to register their marriage. I will be using @citeR to simulate, test and analyse this data. I will download the data from @opendatatoronto.



# Data {#sec-data}

Some of our data is of penguins (@@fig-marriage), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Figure of Marriages in 2023
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()
```

Talk more about it.

# Discussion

## Why are people getting married in North York? {#sec-first-point}

A majority of marriages were registered in North York.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


